---
title: "class08"
author: "Benjamin Cho"
date: "April 25, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## K-means clustering

Start with an example of running **kmeans()** function

```{r}
tmp <- c(rnorm(30,-3), rnorm(30,3))
x <- cbind(x=tmp, y=rev(tmp))
plot(x)
```

Use the kmeans() function setting k to 2 and nstart=20
Inspect/print the results
Q. How many points are in each cluster?
30
Q. What ‘component’ of your result object details
 - cluster size?
 
 - cluster assignment/membership?
 - cluster center?
Plot x colored by the kmeans cluster assignment and
 add cluster centers as blue points
 
 
 
```{r}
y <- kmeans(x, centers=2, nstart=20)
y
y$size
y$cluster
```


```{r}
#plotting with color by the clustering
plot(x,col=y$cluster)
```
 
 
 ## heirarchical Clustering example
 
 We must give the **hclust()** function a distance matrix not the raw data as input
 
```{r}
#distance matrix calculation
d <- dist(x)
d
#clustering
hc <- hclust(d)
plot(hc)
```
 
 
```{r}
cutree(hc, k=2)
```
 
 
 
 
 # Step 1. Generate some example data for clustering
x <- rbind(
 matrix(rnorm(100, mean=0, sd = 0.3), ncol = 2), # c1
 matrix(rnorm(100, mean = 1, sd = 0.3), ncol = 2), # c2
 matrix(c(rnorm(50, mean = 1, sd = 0.3), # c3
 rnorm(50, mean = 0, sd = 0.3)), ncol = 2))
colnames(x) <- c("x", "y")
# Step 2. Plot the data without clustering
plot(x)
# Step 3. Generate colors for known clusters
# (just so we can compare to hclust results)
col <- as.factor( rep(c("c1","c2","c3"), each=50) )
plot(x, col=col)

```{r}
x <- rbind(
 matrix(rnorm(100, mean=0, sd = 0.3), ncol = 2), # c1
 matrix(rnorm(100, mean = 1, sd = 0.3), ncol = 2), # c2
 matrix(c(rnorm(50, mean = 1, sd = 0.3), # c3
 rnorm(50, mean = 0, sd = 0.3)), ncol = 2))
colnames(x) <- c("x", "y")
plot(x)
col <- as.factor( rep(c("c1","c2","c3"), each=50) )
plot(x, col=col)
```

Q. Use the dist(), hclust(), plot() and cutree()
 functions to return 2 and 3 clusters
Q. How does this compare to your known 'col' groups?

```{r}
d <- dist(x)
hc <- hclust(d)
plot(hc)
abline(h=2, col="red")
```

```{r}
hc2 <- cutree(hc, k=2)
hc3 <- cutree(hc, k=3)
```

```{r}
plot(x, col=hc3)
```


# PCA: Principal Component Analysis


```{r}
mydata <- read.csv("https://tinyurl.com/expression-CSV",
 row.names=1) 
mydata
```
 

```{r}
nrow(mydata)
```

```{r}
ncol(mydata)
colnames(mydata)
```


Running PCA on transpose data t()
```{r}
pca <- prcomp(t(mydata), scale=TRUE) 
```


```{r}
attributes(pca)
```


```{r}
plot(pca$x[,1], pca$x[,2]) 
```




```{r}
pca.var <- pca$sdev^2
pca.var.per <- round(pca.var/sum(pca.var)*100, 1) 

pca.var.per
barplot(pca.var.per, main="Scree Plot",
 xlab="Principal Component", ylab="Percent Variation")
```


```{r}
colvec <- colnames(mydata)
colvec[grep("wt", colvec)] <- "red"
colvec[grep("ko", colvec)] <- "blue"
plot(pca$x[,1], pca$x[,2], col=colvec, pch=16,
 xlab=paste0("PC1 (", pca.var.per[1], "%)"),
 ylab=paste0("PC2 (", pca.var.per[2], "%)")) 
```

```{r}
x <- read.csv("UK_foods.csv")
```

```{r}
nrow(x)
ncol(x)
head(x)
```

```{r}
rownames(x) <- x[,1]
x <- x[,-1]
head(x)
```


```{r}
barplot(as.matrix(x), beside=F, col=rainbow(nrow(x)))

```

```{r}
pairs(x, col=rainbow(10), pch=16)
```

```{r}
pca <- prcomp(t(x))
pca
summary(pca)
```




```{r}
plot(pca$x[,1], pca$x[,2], xlab="PC1", ylab="PC2", xlim=c(-270,500))
text(pca$x[,1], pca$x[,2], colnames(x), col = )
```
```{r}
cols <- c("orange", "red", "blue", "darkgreen")
```

```{r}
plot(pca$x[,1], pca$x[,2], xlab="PC1", ylab="PC2", xlim=c(-270,500))
text(pca$x[,1], pca$x[,2], colnames(x), col = cols)
```


#Digging Deeper (variable loadings)

```{r}
par(mar=c(10, 3, 0.35, 0))
barplot( pca$rotation[,1], las=2 )
```

