---
title: "Class12"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(bio3d)
```


```{r}
file.name <- get.pdb("1hsg")
```

```{r}
hiv <- read.pdb(file.name)
hiv
```

Q1: What is the name of the two non protein resid values in this structure? What does resid
correspond to and how would you get a listing of all reside values in this structure? 
HOH, MK1

```{r}
prot <- trim.pdb(hiv, "protein")
lig <-  trim.pdb(hiv, "ligand")
```



```{r}
write.pdb(prot, file="1hsg_protein.pdb")
write.pdb(lig, file="1hsg_ligand.pdb")
```

Load protein file onto autodock


Q2: Can you locate the binding site visually? Note that
crystal structures normally lack hydrogen atoms, why?
They're too small


Q3: Look at the charges. Does it make sense (e.g. based on your knowledge of the
physiochemical properties of amino acids)?
Yes, the Carbons are positively charged?


```{r}
library(bio3d)
```


```{r}
res <- read.pdb("all.pdbqt", multi=TRUE)
```

```{r}
write.pdb(res, "results.pdb")
```

```{r}
# res <- read.pdb("all.pdbqt", multi=TRUE)
ori <- read.pdb("ligand")
rmsd(ori, res)
```



```{r}
library(bio3d)
pdb <- read.pdb("1HEL")
modes <- nma(pdb)
plot(modes, sse=pdb)

```

```{r}
mktrj(modes, mode=7, file="nma_7.pdb")
```

