---
title: "class07"
author: "Benjamin Cho"
date: "April 23, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# fUNCTIONS REVISTED

```{r}
source("http://tinyurl.com/rescale-R")
```

```{r}
rescale(1:10)
```

Try the rescale2() function that catches string inputs
```{r}
rescale2(c(1:10), "string")
```

```{r}
x <- c( 1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, 4)
```

```{r}
is.na(x)
```

```{r}
is.na(y)
```

```{r}
is.na(x) & is.na(y)
```

Take the sum() to find out how many TRUE values we have and thus how many NAs we had in both x and y


```{r}
sum(is.na(x) & is.na(y))
```

Now I can make this into our first function
```{r}
both_na <- function(x,y) {
  sum(is.na(x) & is.na(y))
}
```

```{r}
both_na(x,c(NA,3,NA,2, NA))
```

Test
```{r}
x <- c(NA, NA, NA)
y1 <- c( 1, NA, NA)
y2 <- c( 1, NA, NA, NA)
```

```{r}
both_na(x,y2)

#it matches the shorter object to make it the same length of the longer one. It will recycle back the shorter object
```

```{r}
y3 <- c(1, NA, NA, NA, NA, NA)
both_na(x,y3)
```

```{r}
#tell me if they are equal
3==3

3>2
# not equal
3 != 2
```

```{r}
length(x)
```
```{r}
length(x) != length(y2)
```
now lets try the both_na2 function because it was a different length
```{r}
both_na2(x,y2)
```

```{r}
which(c(F,F,T,F, T))

#which parts of the vector are true
which(is.na(c(1,2,NA, 4)))
```

```{r}
x <- c( 1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, NA)

both_na3(x,y)
```


# Intersect functions

```{r}
df1
```

```{r}
df2
```

```{r}
x <- df1$IDs
y <- df2$IDs

x
y
```

```{r}
?intersect
```
```{r}
intersect(x,y)
```

```{r}
which(x %in% y)
```
```{r}
y[y%in%x]
```
A working snippet

Use Rstudio shortcut CODE > EXTRACT FUNCTION to turn our code into a function
```{r}
gene_intersect <- function(x, y) {
  cbind( x[ x %in% y ], y[ y %in% x ] )
}
```

```{r}
gene_intersect(df1$exp,df1$exp)
```
gene_intersect2(df1,df2)
```{r}
gene_intersect2(df1,df2)
```

```{r}
gene_intersect3(df1,df2)
```



```{r}
merge(df1,df2,by="IDs")
```

Find the average grade dropping the worst homework score

```{r}
grade <- function(x) {
  exclude<-x[x != min(x)]
  mean(exclude)
}
```

```{r}
bob<- c(100,100,100,100,100, 100, 100, 90)
grade(bob)
```

You install.package a package once, but you have to use library to be able to retrieve the function
```{r}

```






